Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-28 Paper/RSVOptimization.rnw
Bumped draft #
Pagination
Figure placement
Promoting 1-week rounding to main analysis

\usepackage[hidelinks]{hyperref}
\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
\usepackage{tikz}
\usepackage{draftwatermark}
\SetWatermarkScale{1}
\SetWatermarkAngle{45}
\SetWatermarkFontSize{4ex}
\SetWatermarkHorCenter{12ex}
\SetWatermarkVerCenter{12ex}
\SetWatermarkLightness{.5}
\SetWatermarkText{DRAFT 1}

@@

@@

@@

\begin{figure}[b]
\begin{center}
\input{\figuresDir/coverageByRegionAAPInsight.tex}
\caption[County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
\label{fig:coverageByRegionAAPInsight}
\end{center}
\end{figure}

@@

% TODO Update results to 1-week rounding

The six spatially-adjusted prophylaxis regimens, yield results in all counties that are as good or better than the AAP guidelines. (Figure \ref{fig:coverageByRegionRegimen}). Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}). The alternative regimen based on statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results. Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on county-level offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable. In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.

>>>>

\usepackage[hidelinks]{hyperref}
\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
\usepackage{tikz}
\usepackage{draftwatermark}
\SetWatermarkScale{1}
\SetWatermarkAngle{45}
\SetWatermarkFontSize{4ex}
\SetWatermarkHorCenter{12ex}
\SetWatermarkVerCenter{12ex}
\SetWatermarkLightness{.5}
\SetWatermarkText{DRAFT 2}

@@

\begin{samepage}

@@

\end{samepage}

@@

\begin{figure}
\begin{center}
\input{\figuresDir/coverageByRegionAAPInsight.tex}
\caption[County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
\label{fig:coverageByRegionAAPInsight}
\end{center}
\end{figure}

@@

The six spatially-adjusted prophylaxis regimens yield results in all counties that are as good or better than the AAP guidelines. (Figure \ref{fig:coverageByRegionRegimen}). Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}). The least favorable of our alternative regimens --- based on statewide onset --- yields the increase to \Sexpr{regionStrategyCoverage("all", "stateOnset", 1)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 1, level)}); other alternative regimens yield similar results. Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the least favorable of our alternative regimens --- based on county-level offset --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 1, level)}), with other alternative regimens being comparable. In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.
